DNA meth and IVF

### 2024-01-03 figs/art_example.Rmd
dont use ftp

tic()
new.hgnc.table <- getCurrentHumanMap()
fix <- checkGeneSymbols(gt2$gene,map=new.hgnc.table)
fix2 <- fix[which(fix$x != fix$Suggested.Symbol),]
length(unique(fix2$x))
gt2$gene <- fix$Suggested.Symbol
toc()

>>>>

tic()
#new.hgnc.table <- getCurrentHumanMap()
fix <- checkGeneSymbols(gt2$gene,map=new.hgnc.table)
fix2 <- fix[which(fix$x != fix$Suggested.Symbol),]
length(unique(fix2$x))
gt2$gene <- fix$Suggested.Symbol
toc()
